### 2021-03-12 README.Rmd
README update
Adding code coverage

[![Build Status](https://github.com/rudeboybert/forestecology/workflows/R-CMD-check/badge.svg)](https://github.com/rudeboybert/forestecology/actions)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/forestecology)](https://cran.r-project.org/package=forestecology)

@@

```{r}
library(tidyverse)
library(forestecology)
library(blockCV)
library(patchwork)
```

@@

<!--For fuller examples on actual datasets see ___.-->

>>>>

[![Build Status](https://github.com/rudeboybert/forestecology/workflows/R-CMD-check/badge.svg)](https://github.com/rudeboybert/forestecology/actions)
[![Codecov test coverage](https://codecov.io/gh/rudeboybert/forestecology/branch/master/graph/badge.svg)](https://codecov.io/gh/rudeboybert/forestecology?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/forestecology)](https://cran.r-project.org/package=forestecology)

@@

```{r}
library(tidyverse)
library(forestecology)
library(patchwork)
library(blockCV)

# Resolve conflicting functions
filter <- dplyr::filter
```

@@
